The transition redshift as a probe of reionization

### 2019-08-09 paper/ms.tex
Small changes
Add beginning of methods section

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[The Transition Redshift]{The transition redshift as a probe of reionization}

@@

@@

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

>>>>

\newcommand{\tfast}{\texttt{21cmFAST}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[The transition redshift]{The transition redshift as a probe of reionization}

@@

\section{Methods}
\subsection{21cmFAST}
We generate realizations of the 21~cm field for our different EoR models using
the publicly available code \tfast{}
v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST},
commit: \texttt{42e7566}}. Spin temperature fluctuations are computed and the
excursion set approach is used to identify the ionized regions
\citep{2011MNRAS.411..955M}.

@@

\bibliographystyle{mnras}
\bibliography{references} % if your bibtex file is called example.bib
